Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-21 paper/paper.tex
addressing of checkpoints

This way, each occurrence of a checkpoint has unique address,
but small disturbances (like removal or addition of a single
checkpoint with a particular identifier) are
unlikely to derail the entire sequence.

>>>>

This way, each occurrence of a checkpoint has unique address,
but small disturbances --- removal or addition of a single or just
a few checkpoints --- are unlikely to derail the entire sequence.
The probability of derailment depends on the padding. The
padding can be safely, and without any impact on performance,
set to rather large numbers. However, rounding up to a multiple
of 16 proved to be appropriate for all practical purposes.

Function \texttt{checkpoint-id} in the
\texttt{anglican.inference} namespace automates generation of
checkpoint addresses and can be used from any inference
algorithm.
